Understanding Alternate Alleles in 1,000 Genomes VCF Data
========================================================

We know from the [FAQ](http://www.1000genomes.org/faq/are-all-genotype-calls-current-release-vcf-files-bi-allelic) that the 1,000 Genomes VCF data is [bi-allelic](http://www.1000genomes.org/faq/are-all-genotype-calls-current-release-vcf-files-bi-allelic) → meaning that each row in the source VCF has only one value in the ALT field.  So for each sample in a row, the genotype was called as either the reference or the single ALT value.  At any particular position in the genome we can have much more variation than a single alternate, so we need to understand how that is encoded in this data set.

_Let’s explore the question “Is (contig, position, reference_bases) a unique key in the 1,000 Genomes Data?”_

For query [chrom-pos-ref-dups.sql](./chrom-pos-ref-dups.sql)

```{r initialize, echo=FALSE, warning=FALSE, cache=TRUE}
require(bigrquery)
sql = readChar('./chrom-pos-ref-dups.sql',
               nchars=1e6)
cat(sql)
billing_project = "google.com:biggene" # put your projectID here
result = query_exec(project="google.com:biggene", dataset="1000genomes", query=sql, billing = billing_project)
```

We see tabular results:
```{r echo=FALSE}
print(result)
```