Exploring the phenotypic data
========================================================

Note that the full 1,000 dataset has data for 3,500 individuals but the variants in table variants1kG are only for a subset of those individuals.  Let’s explore the phenotypic traits for the individuals whose variant data we do have.

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment=NA}
require(bigrquery)
require(xtable)
billing_project = 'google.com:biggene' # put your projectID here
```

How many sample are we working with in this variant dataset?
```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, comment=NA}
sql = readChar('./num-samples.sql',
               nchars=1e6)
cat(sql)
result = query_exec(project='google.com:biggene', dataset='1000genomes', query=sql, billing = billing_project)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, results='asis'}
print(xtable(head(result)), type = 'html', include.rownames = F)
```
So for analyses across all samples, the sample size is 1,092.

What is the gender ratio?
```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, comment=NA}
sql = readChar('./gender-ratio.sql',
               nchars=1e6)
cat(sql)
result = query_exec(project='google.com:biggene', dataset='1000genomes', query=sql, billing = billing_project)
```


```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, results='asis'}
print(xtable(head(result)), type = 'html', include.rownames = F)
```
So for analyses across genders the sample size is roughly even.

What are the ratios of ethnicities?



```{r echo=FALSE, message=FALSE, warning=FALSE, comment=NA, results='asis'}
cat(paste('Number of rows in result:', nrow(result), '\n'))
```


TODO(deflaux): more here